---
title: "EXAMPLE"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---
You open a new flexboard by choosing "flexdashboard" from templates 

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(tidyverse)

```

Add a sidebar showing up on all pages (use simple dashes for a single sidebar) {.sidebar}
=======================
Eerything that goes into the sidebar

# First example

Just using one hasgtag is a way of creating a whole new flexdashboard

Column {data-width=350}
-----------------------------------------------------------------------

### Chart A

```{r, fig.height=12}

ggplot(mpg, aes(displ, cyl)) +
  geom_point(color = "gray70") +
  geom_smooth() +
  theme_minimal() +
  labs(title = "First plot") 

```

Column {.tabset fig.height=18}
-----------------------------------------------------------------------

Two more charts

### Chart B

```{r}

ggplot(mpg, aes(displ, cyl)) +
  geom_point(color = "gray70") +
  geom_smooth() +
  theme_bw() +
  facet_wrap(~trans) +
  labs(title = "Second plot")

```

### Chart C

```{r}

ggplot(mpg, aes(displ, cyl)) +
  geom_point(color = "gray70") +
  geom_smooth() +
  theme_bw() +
  facet_wrap(~manufacturer) +
  labs(title = "Third plot") 
```


# Second example

Column {data-width=350}
-----------------------------------------------------------------------

### Chart A

```{r, fig.height=12}

library(ggplot2)
ggplot(mpg, aes(displ, cyl)) +
  geom_point(color = "gray70") +
  geom_smooth() +
  theme_minimal() +
  labs(title = "First plot")

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

ggplot(mpg, aes(displ, cyl)) +
  geom_point(color = "gray70") +
  geom_smooth() +
  theme_bw() +
  facet_wrap(~trans) +
  labs(title = "Second plot")

```

### Chart C

```{r}

ggplot(mpg, aes(displ, cyl)) +
  geom_point(color = "gray70") +
  geom_smooth() +
  theme_bw() +
  facet_wrap(~manufacturer) +
  labs(title = "Third plot") 
```

Column {data-width=300}
-----------------------------------------------------------------------

### Chart D

```{r,fig.height=12}

ggplot(mpg, aes(displ, cyl)) +
  geom_point(color = "gray70") +
  geom_smooth() +
  theme_bw() +
  facet_wrap(~trans) +
  labs(title = "Fourth plot")

```

Publishing your flexdashboard: Create repo on Githib without any lisence or read me